Speed and strength of an epidemic intervention

### 2020-02-27 doc/speedstrength.tex
format

\maketitle

@@

>>>>

\begin{flushleft}{
	\Large
	\textbf\newline{
		Speed and strength of an epidemic intervention
	}
}
\newline
\\
Jonathan Dushoff\textsuperscript{1,2,3,*}
Sang Woo Park\textsuperscript{4}
\\
\bigskip
\textbf{1} Department of Biology, McMaster University, Hamilton, ON, Canada
\\
\textbf{2} Department of Mathematics and Statistics, McMaster University, Hamilton, ON, Canada
\\
\textbf{3} M.\,G.\,DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, ON, Canada
\\
\textbf{4} Department of Ecology and Evolutionary Biology, Princeton University, Princeton, NJ, USA
\\
\bigskip

*Corresponding author: dushoff@mcmaster.ca
\end{flushleft}

@@

\pagebreak
